term papaer 2

### 2024-02-11 outputs/paper/paper.qmd
paper

@@

```{r}
#| label: tbl-terc
#| tbl-cap: "Dividing respondents into three terciles by their municipality's gender ratio"
#| echo: false
#| message: false
#| warning: false

@@

```{r}
#| label: tbl-stmt
#| tbl-cap: "Statements used for surveying respondents"
#| echo: false
#| message: false
#| warning: false

>>>>

This paper will replicate the survey data that was originally collected for

@@

```{r}
#| label: figl-terc
#| fig-cap: "Dividing respondents into three terciles by their municipality's gender ratio"
#| echo: false
#| message: false
#| warning: false

@@

```{r}
#| label: fig-ecoil
#| fig-cap: unemployment 
#| echo: false
#| message: false
#| warning: false
